---
title: "MS_4"
author: "JBR"
date: "3/7/2020"
output: html_document
---
```{r, include = FALSE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(gt)
library(ggplot2)
library(tidycensus)
library(readxl)

options(scipen=999)
 income <- get_acs(geography = "county",
  variables = "B19013_001",
  table = NULL,
  cache_table = FALSE,
  year = 2018,
  endyear = NULL,
  output = "tidy",
  state = NULL,
  county = "New York",
  geometry = FALSE,
  keep_geo_vars = FALSE,
  shift_geo = FALSE,
  summary_var = NULL,
  key = NULL,
  moe_level = 90,
  survey = "acs5",
  show_call = FALSE,
)
 
 
```


```{r, include = FALSE}
crime <- read_xlsx("cs-en-us-city-2.xlsx") 
```





Thus far, I have worked with the two data sets I mentioned in my last milestone. Due to issues with anonymizing the main dataset, I might need to pivot on my project. Currently, I have read in OPEN DATA NYC crime excels on crime in NYC, and am working with the census data we use in class to create race maps in NYC. I cannot put the main dataset (gamerbase) in the milestone yet, but I will provide an update on this by Monday afternoon at 6pm. 

